### 2017-10-09 TF-vldb2018/sec-tsim.tex

\sstab(2) Different from strong simulation with a fixed radius for balls (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is auto-adjustable, having a user specified upper bound only.

>>>>

\sstab(2) Different from strong simulation with a fixed radius for balls (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of balls is auto-adjustable, having a user specified upper bound only.
